---
title: "toonCat_SI_FiguresTables"
author: "Jewelia K. Yao"
date: '`r Sys.Date()`'
output: html_document
---

TOONCAT SUPPLEMENTARY FIGURES AND TABLES
Supplementary tables and figures, in order of reference, for the toonCat manuscript. Includes only the R generated plots, but other figures are noted. See MATLAB scripts and figures folder for other figure components.

```{r Setup, warning=F, message=F, echo=FALSE}
# Setup file
source("~./code/toonCat_analysisSetup.R")

# Set global variables
output_directory <- "./results/supplementary/"
LMM_filters <- c("hemi != 'mh'", "hemi != 'zh'", "ROI != 'blank'","ROI != 'blank1'", "category != 'word'", "category != 'words'")
ventralLMM_filters <- c("hemi != 'mh'", "hemi != 'zh'", "ROI != 'blank'","ROI != 'blank1'", "stream == 'ventral'")
retinotopyLMM_filters <- c("ROI %in% c('V1', 'V2', 'V3')", "hemi != 'mh'", "hemi != 'zh'")
```


# FUNCTIONS

```{r}
run_and_format_analysis <- function(analysis_list, file_path, file_name, bold_p_value = 0.05, digits = 3) {

  # Helper function to process individual analyses
  run_LMM_analysis <- function(data, formula, filters = NULL, analysis_name) {
  # Apply filters dynamically if provided
  if (!is.null(filters) && length(filters) > 0) {
    filtered_data <- data %>%
      filter(!!!rlang::parse_exprs(filters)) %>%
      na.omit()
  } else {
    filtered_data <- data %>%
      na.omit()
  }

  # Fit the model and perform joint tests
  model <- lmerTest::lmer(formula, data = filtered_data)
  results <- joint_tests(model)

  # Add the analysis name as a column
  results <- results %>%
    mutate(Analysis = analysis_name)

  return(results)
}


  # Process each analysis
  combined_results <- bind_rows(lapply(analysis_list, function(analysis) {
    run_LMM_analysis(
      data = analysis$data,
      formula = analysis$formula,
      filters = analysis$filters,
      analysis_name = analysis$analysis_name
    )
  }))

  # Define the format and save function
  format_and_save_table <- function(results, file_path, bold_p = TRUE, bold_p_value, digits) {
    # Format p-values and F-ratios
    format_p <- function(p) {
      ifelse(p < 0.0001, format(p, scientific = TRUE, digits = 4), format(p, nsmall = 3))
    }
    format_F <- function(Fval) {
      format(Fval, nsmall = digits)
    }

    # Reorder columns to make "Analysis" the first column
    formatted_results <- results %>%
      mutate(
        p.value = as.numeric(p.value),
        p.value = sapply(p.value, format_p),
        F.ratio = sapply(F.ratio, format_F)
      ) %>%
      select(Analysis, everything()) %>%  # Ensure Analysis is the first column
      group_by(Analysis) %>%
      mutate(Analysis = ifelse(row_number() == 1, Analysis, "")) %>%  # Show Analysis name only in the first row
      ungroup()

    # Identify the rows where a new analysis starts (first row of each analysis group)
    add_space_rows <- which(formatted_results$Analysis != "")

    # Generate the table
    table <- formatted_results %>%
      kable(format = "latex", booktabs = TRUE, digits = digits) %>%
      kable_classic(full_width = FALSE, html_font = "Calibri")

    # Add spacing above rows where a new analysis starts (excluding the first analysis)
    for (row in add_space_rows[-1]) {  # Skip the first analysis row
      table <- table %>%
        row_spec(row, extra_css = "border-top: 10px solid white;")
    }

    # Apply bolding conditionally based on `bold_p`
    if (bold_p) {
      table <- table %>%
        row_spec(which(as.numeric(formatted_results$p.value) < bold_p_value), bold = TRUE)
    }

    # Save the table
    save_kable(table, file = file_path, zoom = 3, density = 500)

    return(formatted_results)  # Return the formatted results in case further use is needed
  }

  # Construct full file paths
  bold_file_path <- file.path(file_path, paste0(file_name, "_bold.tex"))
  no_bold_file_path <- file.path(file_path, paste0(file_name, ".tex"))

  # Save bolded table
  # formatted_results_bold <- format_and_save_table(
  #   results = combined_results,
  #   file_path = bold_file_path,
  #   bold_p = TRUE,
  #   bold_p_value = bold_p_value,
  #   digits = digits
  # )

  # Save non-bolded table
  formatted_results_no_bold <- format_and_save_table(
    results = combined_results,
    file_path = no_bold_file_path,
    bold_p = FALSE,
    bold_p_value = bold_p_value,
    digits = digits
  )

  # Return combined results and paths to saved files
  return(list(
    combined_results = combined_results,
   # bold_output_file = bold_file_path,
    no_bold_output_file = no_bold_file_path
  ))
}
```

```{r}
run_and_format_betas <- function(analysis_list, file_path, file_name,
                                 bold_p_value = 0.05, digits = 3,
                                 ci_level = 0.95) {

  suppressPackageStartupMessages({
    library(dplyr)
    library(tidyr)
    library(kableExtra)
    library(knitr)
    library(lmerTest)
    library(broom.mixed)
    library(emmeans)
    library(rlang)
  })

  # ---------------- Helper function: run one LMM ----------------
  run_LMM_betas <- function(data, formula, filters = NULL, analysis_name) {

    # Apply filters dynamically if provided
    if (!is.null(filters) && length(filters) > 0) {
      filtered_data <- data %>%
        dplyr::filter(!!!rlang::parse_exprs(filters)) %>%
        tidyr::drop_na()
    } else {
      filtered_data <- data %>% tidyr::drop_na()
    }

    # Fit the model
    model <- lmerTest::lmer(formula, data = filtered_data)

    # Extract fixed effects
    results <- broom.mixed::tidy(
      model, effects = "fixed", conf.int = TRUE, conf.level = ci_level
    ) %>%
      transmute(
        Analysis = analysis_name,
        Term     = term,
        Beta     = estimate,
        SE       = std.error,
        df       = df,
        t        = statistic,
        p.value  = p.value,
        CI_low   = conf.low,
        CI_high  = conf.high
      )

    return(results)
  }

  # ---------------- Run all analyses ----------------
  combined_results <- bind_rows(lapply(analysis_list, function(analysis) {
    run_LMM_betas(
      data = analysis$data,
      formula = analysis$formula,
      filters = analysis$filters,
      analysis_name = analysis$analysis_name
    )
  }))

  # ---------------- Formatting and Saving ----------------
  format_and_save_table <- function(results, file_path, bold_p = TRUE,
                                    bold_p_value, digits) {

    p_numeric <- results$p.value

    # ---- P-value formatter (always show scientific small p's) ----
    format_p <- function(p) {
      vapply(p, function(x) {
        if (is.na(x)) return("")
        if (x < .Machine$double.xmin || x == 0) {
          return("<2.2e-308")
        } else if (x < 1e-4) {
          return(formatC(x, format = "e", digits = 3))
        } else {
          return(formatC(x, format = "f", digits = 3))
        }
      }, character(1))
    }

    format_num <- function(x) format(round(x, digits), nsmall = digits)
    format_ci <- function(lo, hi, dig = digits) {
      paste0("[", format(round(lo, dig), nsmall = dig), ", ",
                  format(round(hi, dig), nsmall = dig), "]")
    }

    formatted_results <- results %>%
      mutate(
        Beta    = format_num(Beta),
        SE      = format_num(SE),
        df      = ifelse(is.na(df), "", format(round(df, 1), nsmall = 1)),
        t       = format_num(t),
        p.value = as.character(format_p(p.value)),
        CI      = format_ci(CI_low, CI_high, digits)
      ) %>%
      select(Analysis, Term, Beta, SE, df, t, p.value, CI) %>%
      group_by(Analysis) %>%
      mutate(Analysis = ifelse(row_number() == 1, Analysis, "")) %>%
      ungroup()

    add_space_rows <- which(formatted_results$Analysis != "")

    table <- formatted_results %>%
      kable(format = "latex", booktabs = TRUE, digits = digits,
            col.names = c("Analysis", "Term", "β", "SE", "df", "t", "p", "95% CI")) %>%
      kable_classic(full_width = FALSE, html_font = "Calibri") %>%
      column_spec(1, bold = TRUE)

    if (length(add_space_rows) > 1) {
      for (row in add_space_rows[-1]) {
        table <- table %>% row_spec(row, extra_css = "border-top: 10px solid white;")
      }
    }

    if (bold_p) {
      bold_rows <- which(p_numeric < bold_p_value)
      if (length(bold_rows)) {
        table <- table %>% row_spec(bold_rows, bold = TRUE)
      }
    }

    save_kable(table, file = file_path, zoom = 3, density = 500)
    invisible(formatted_results)
  }

  # ---------------- Save bolded and non-bolded versions ----------------
  bold_file_path    <- file.path(file_path, paste0(file_name, "_betas_bold.tex"))
  no_bold_file_path <- file.path(file_path, paste0(file_name, "_betas.tex"))

  # formatted_results_bold <- format_and_save_table(
  #   combined_results, bold_file_path, bold_p = TRUE,
  #   bold_p_value = bold_p_value, digits = digits
  # )

  formatted_results_no_bold <- format_and_save_table(
    combined_results, no_bold_file_path, bold_p = FALSE,
    bold_p_value = bold_p_value, digits = digits
  )

  list(
    combined_results = combined_results,
   # bold_output_file = bold_file_path,
    no_bold_output_file = no_bold_file_path
  )
}

```




# Supplementary Figure 1. Phase maps for all participants
See figure folder

# Supplementary Figure 2. Eccentricity maps for all participants
See figure folder

# Supplementary Figure 3. Size maps for all participants
See figure folder

# Supplementary Table 1. V1, V2, V3 statistics
```{r, warning=F, message=F, echo=FALSE}
S.Table1_V1V2V3 <- list(
  list(
    data = df.centers,
    formula = centerX ~ group*ROI*hemi + (1|sub),
    filters = retinotopyLMM_filters,
    analysis_name = "LMM: pRF centers X-position (Age Group)"
  ),
    list(
    data = df.centers,
    formula = centerY ~ group*ROI*hemi + (1|sub),
    filters = retinotopyLMM_filters,
    analysis_name = "LMM: pRF centers Y-position (Age Group)"
  ),
    list(
    data = df.centers,
    formula = centerR ~ group*ROI*hemi + (1|sub),
    filters = retinotopyLMM_filters,
    analysis_name = "LMM: pRF centers Eccentricity (Age Group)"
  ),
    list(
    data = df.centers,
    formula = size ~ group*ROI*hemi + (1|sub),
    filters = retinotopyLMM_filters,
    analysis_name = "LMM: pRF size (Age Group)"
  )
)

# Run the function
output <- run_and_format_analysis(
  analysis_list = S.Table1_V1V2V3,
  file_path = output_directory,
  file_name = "S.Table1_V1V2V3",
  bold_p_value = 0.05,
  digits = 3
)

# Betas format
# output <- run_and_format_betas(
#   analysis_list = S.Table1_V1V2V3,
#   file_path = output_directory,
#   file_name = "S.Table1_V1V2V3",
#   bold_p_value = 0.05,
#   digits = 3
# )

```


# Supplementary Table 2. pRF size vs eccentricity statistics
```{r, warning=F, message=F, echo=FALSE}

S.Table2_sizeVecc <- list(
  list(
    data = df.sizeEcc_ret,
    formula = slope ~ group*ROI*hemi + (1|sub),
    filters = NULL,
    analysis_name = "LMM: Size v. Ecc Slopes"
  ),
  list(
    data = df.sizeEcc_ret,
    formula = intercept ~ group*ROI*hemi + (1|sub),
    filters = NULL,
    analysis_name = "LMM: Size v. Ecc Intercepts"
  )
)

# Run the function
output <- run_and_format_analysis(
  analysis_list = S.Table2_sizeVecc,
  file_path = output_directory,
  file_name = "S.Table2_sizeVecc_slopes_intercepts",
  bold_p_value = 0.05,
  digits = 3
)

# Betas format
# output <- run_and_format_betas(
#   analysis_list = S.Table2_sizeVecc,
#   file_path = output_directory,
#   file_name = "S.Table2_sizeVecc_slopes_intercepts",
#   bold_p_value = 0.05,
#   digits = 3
# )
```

# Supplementary Table 3. Number of individuals with ROI per group
```{r}
# Create summary table
summary_table <- df.CoV_cat_latdors %>%
  na.omit() %>%
  filter(hemi %in% c("lh", "rh")) %>%
  group_by(ROI, hemi, group) %>%
  summarise(N = n_distinct(subject), .groups = "drop") %>%
  pivot_wider(
    names_from = c(group, hemi), 
    values_from = N) %>%
  mutate(ROI = stringr::str_replace_all(ROI, "_", "-"),
         ROI = stringr::str_replace_all(ROI, "limbs", "bodies"),
         adolescents_rh = ifelse(ROI == "mOTS-words", " ", adolescents_rh),
         Adults_rh = ifelse(ROI == "mOTS-words", " ", Adults_rh),
         ROI = ifelse(ROI == "pSTS-faces", "pSTS-faces*", ROI),
         ROI = ifelse(ROI == "MTG-bodies", "MTG-bodies*", ROI))

# Define headers with subcolumns for hemispheres under each measure
measure_headers <- c(
  " " = 1, "Left Hemisphere" = 2, "Right Hemisphere" = 2)

# Manually set column names
colnames(summary_table) <- c(
  "ROI", "adolescents", "Adults", "adolescents", "Adults")

# Create HTML tables
count_table <- summary_table %>%
  kbl(format = "latex", caption = "",  align=('lcccc')) %>%
  kable_classic(full_width = F, html_font = "Calibri") %>%
  row_spec(7, extra_css = "padding-bottom: 30px;") %>% 
  row_spec(11, extra_css = "padding-bottom: 30px;") %>%
  add_header_above(measure_headers, extra_css = "font-size: 10px;") %>%
 save_kable(file = file.path(output_directory, "S.Table3_ROI_counts.tex"),
            zoom = 3, 
            density = 500)

# Save the table to a CSV file
# csv_path <- file.path(output_directory, "S.Table3_ROI_counts.csv")
# write.csv(summary_table, file = csv_path, row.names = FALSE)
```

# Supplementary Table 4. Proportion of voxels with VE > 20% statistics
```{r, warning=F, message=F, echo=FALSE}

S.Table4_proportionVE20 <- list(
  list(
    data = df.CoV_cat_latdors,
    formula = proportion20 ~ group*stream*category*hemi + (1|sub),
    filters = LMM_filters,
    analysis_name = "LMM: Proportion Voxels with Variance Explained > 20%"
  ),
  list(
    data = df.CoV_cat_latdors,
    formula = proportion20 ~ group*category*hemi + (1|sub),
    filters = ventralLMM_filters,
    analysis_name = "Ventral LMM: Proportion Voxels with Variance Explained > 20%"
  )
)

# Run the function
output <- run_and_format_analysis(
  analysis_list = S.Table4_proportionVE20,
  file_path = output_directory,
  file_name = "S.Table4_proportionVE20",
  bold_p_value = 0.05,
  digits = 3
)

# Betas format
# output <- run_and_format_betas(
#   analysis_list = S.Table4_proportionVE20,
#   file_path = output_directory,
#   file_name = "S.Table4_proportionVE20",
#   bold_p_value = 0.05,
#   digits = 3
# )
```

# Supplementary Figure 4. pRF x-position
```{r pRF x-position, fig.width=12, fig.height=4, warning=F, message=F, echo=FALSE}
png(file.path(output_directory, "S.F4_pRFcenters_xPosition_violin.png"), units="in", width=15, height=2.25, res=300)
df.centers_cat %>%
  ggplot(., aes(x = interaction(group, hemi, sep = "."), 
                y = centerX, 
                color = ROI, 
                fill = ROI, 
                alpha = hemi)) +
  geom_violin(position = position_dodge(width = 0.8), na.rm = TRUE) + 
  geom_point(size = 0.5, na.rm = TRUE) +
  stat_summary(fun.y = mean,
               geom = "pointrange", 
               color = "black") +
  stat_summary(fun.data = mean_se, 
               geom = "errorbar", 
               color = "black") +
  geom_hline(yintercept = 0) +
  labs(y = "X Position  (°)") +
  facet_grid(~ ROI) +
  theme(legend.position = "none",
        strip.background = element_blank(),
        strip.text.x = element_blank(),
        axis.title.y=element_text(size=16),
        panel.spacing = unit(0, "null"),
        panel.grid.major.y = element_line(color = "gray96",size = 0.5),
        axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.text.y = element_text(size = 15),
        text = element_text(family = "Avenir")) +
  scale_color_manual(values = roi_colors, na.translate = FALSE) +
  scale_alpha_manual(values = c("lh" = 0.45, "rh" = 0.8)) +
  scale_fill_manual(values = roi_colors, na.translate = FALSE) +
  scale_y_continuous(breaks = seq(-20, 20, 5), limits = c(-21, 21)) 
dev.off()
```

# Supplementary Table 5: Results of KS-tests
Code run in MATLAB (toonCat_calcKSTests_bootbyROI_csv.m) to get csv
```{r}
library(readr)
library(gt)

# ---- 1) Load ----
df <- read_csv("../data/KS_bootstrap_allResults.csv", show_col_types = FALSE)

# ---- 2) Row label "ROI - category" (handles faces/bodies/places/words/limbs) ----
df <- df %>%
  mutate(
    roi_noprefix = sub("^(lh|rh)\\.", "", ROI, perl = TRUE),
    base_roi     = sub("_(faces|bodies|places|words|limbs).*", "", roi_noprefix, perl = TRUE),
    cat_tok      = tolower(sub(".*_(faces|bodies|places|words|limbs).*", "\\1", roi_noprefix, perl = TRUE)),
    has_cat      = grepl("_(faces|bodies|places|words|limbs)", roi_noprefix, perl = TRUE),
    label        = ifelse(has_cat, paste0(base_roi, " - ", cat_tok), base_roi)
  )

# ---- 3) Split to LH/RH and carry Bonferroni thresholds; join side-by-side ----
lhs <- df %>%
  filter(hemi == "lh") %>%
  transmute(
    param, label,
    L_thr   = p_thresh_stream,
    LH_Mean = KS_effect_mean,
    # CI with two decimals now; keep raw numbers here for clean formatting
    LH_CI_lo = KS_effect_CI_low,
    LH_CI_hi = KS_effect_CI_high,
    LH_p     = p_value_KS_bootstrap
  )

rhs <- df %>%
  filter(hemi == "rh") %>%
  transmute(
    param, label,
    R_thr   = p_thresh_stream,
    RH_Mean = KS_effect_mean,
    RH_CI_lo = KS_effect_CI_low,
    RH_CI_hi = KS_effect_CI_high,
    RH_p     = p_value_KS_bootstrap
  )

wide <- full_join(lhs, rhs, by = c("param","label"))

# ---- 4) Enforce requested ROI order (rows) ----
roi_order <- c(
  "pOTS - words","mOTS - words","OTS - bodies","IOG - faces",
  "pFus - faces","mFus - faces","CoS - places","LOS - limbs",
  "ITG - limbs","MTG - limbs","pSTS - faces","MOG - places","IPS - places"
)
wide <- wide %>%
  mutate(label = factor(label, levels = roi_order))

# ---- 5) Optional: explicit parameter order ----
param_order <- c("X","Y","eccen","size")
wide$param <- factor(wide$param, levels = intersect(param_order, unique(wide$param)))
wide <- wide %>% arrange(param, label)

# ---- 6) Formatting helpers ----
# big, bold markers (no HTML)
star_char <- "\u2731"  # ✱ heavy asterisk
dot_char  <- "\u25CF"  # ● black circle (bold "dot")
thin_sp   <- "\u2009"  # thin space

fmt_ci2    <- function(lo, hi) sprintf("(%.2f, %.2f)", lo, hi)
fmt_p_sci2 <- function(x, mark = "", digits = 2) {
  ifelse(
    is.na(x), "—",
    paste0(formatC(x, format = "e", digits = digits),
           ifelse(mark == "", "", paste0(thin_sp, mark)))
  )
}

wide <- wide %>%
  mutate(
    # significance: star if Bonferroni; dot if < .05 but not Bonferroni
    LH_mark = dplyr::case_when(!is.na(LH_p) & LH_p < L_thr ~ star_char,
                               !is.na(LH_p) & LH_p < 0.05  ~ star_char,
                               TRUE                         ~ ""),
    RH_mark = dplyr::case_when(!is.na(RH_p) & RH_p < R_thr ~ star_char,
                               !is.na(RH_p) & RH_p < 0.05  ~ star_char,
                               TRUE                         ~ ""),
    LH_CI_fmt = fmt_ci2(LH_CI_lo, LH_CI_hi),
    RH_CI_fmt = fmt_ci2(RH_CI_lo, RH_CI_hi),
    LH_p_fmt  = fmt_p_sci2(LH_p, LH_mark, digits = 2),
    RH_p_fmt  = fmt_p_sci2(RH_p, RH_mark, digits = 2)
  )

# ---- 7) Keep ONLY display columns ----
wide_tbl <- wide %>%
  select(
    param, label,
    LH_Mean, LH_CI_fmt, LH_p_fmt,
    RH_Mean, RH_CI_fmt, RH_p_fmt
  )

library(knitr)
library(kableExtra)
library(dplyr)

# ---- 8) Build LaTeX table (match other tables) ----

# (A) Make a display version (strings ok; kable will print nicely)
wide_tex <- wide_tbl %>%
  mutate(
    # ensure param is character for grouping
    param = as.character(param)
  )

# (B) For kable, keep "ROI - category" as first column (not rownames)
wide_tex <- wide_tex %>%
  rename(`ROI - category` = label) %>%
  select(
    param, `ROI - category`,
    LH_Mean, LH_CI_fmt, LH_p_fmt,
    RH_Mean, RH_CI_fmt, RH_p_fmt
  )

# (C) Base kable (drop param column in the printed table; we’ll use it for grouping)
kbl_df <- wide_tex %>% select(-param)

kbl <- kbl_df %>%
  kable(
    format = "latex",
    booktabs = TRUE,
    longtable = TRUE,
    escape = FALSE,   # keep ✱ and any symbols
    col.names = c(
      "ROI - category",
      "Mean KS (D)", "95\\% CI", "Bootstrap p",
      "Mean KS (D)", "95\\% CI", "Bootstrap p"
    )
  ) %>%
  kable_styling(latex_options = c("hold_position")) %>%
  add_header_above(
    c(" " = 1, "Left hemisphere" = 3, "Right hemisphere" = 3),
    bold = TRUE
  )

# (D) Add grouped sections by param (X / Y / eccen / size)
# Find row ranges for each param block in the current order
starts <- which(!duplicated(wide_tex$param))
ends   <- c(starts[-1] - 1, nrow(wide_tex))
params <- wide_tex$param[starts]

for (i in seq_along(params)) {
  kbl <- kbl %>%
    pack_rows(index = setNames(ends[i] - starts[i] + 1, params[i]), bold = TRUE)
}

# (E) Add the footnote (PNAS-style note under table)
kbl <- kbl %>%
  kableExtra::footnote(
    general = paste0(
      "✱ Bonferroni-corrected significance (bootstrap p < stream threshold). ",
      "Stream thresholds: Ventral = 0.0038; Lateral/Dorsal = 0.0042."
    ),
    threeparttable = TRUE
  )

# ---- 9) Save .tex ----
file_name <- "S.Table5_KSTest_boostrap"
save_kable(kbl, file = file.path(output_directory, paste0(file_name, ".tex")))

```


# Supplementary Table 6. pRF y-position statistics
```{r, warning=F, message=F, echo=FALSE}

S.Table6_pRFcenters_Y <- list(
  list(
    data = df.centers_cat_latdors,
    formula = centerY ~ group*stream*category*hemi + (1|sub),
    filters = LMM_filters,
    analysis_name = "LMM: pRF centers Y-position (Age Group)"
  ),
  list(
    data = df.centers_cat_latdors,
    formula = centerY ~ group*category*hemi + (1|sub),
    filters = ventralLMM_filters,
    analysis_name = "Ventral LMM: pRF centers Y-position (Age Group)"
  ),
    list(
    data = df.centers_cat_latdors,
    formula = centerY ~ age*stream*category*hemi + (1|sub),
    filters = LMM_filters,
    analysis_name = "LMM: pRF centers Y-position (Age Continuous)"
  ),
  list(
    data = df.centers_cat_latdors,
    formula = centerY ~ age*category*hemi + (1|sub),
    filters = ventralLMM_filters,
    analysis_name = "Ventral LMM: pRF centers Y-position (Age Continuous)"
  )
)

# Run the function
output <- run_and_format_analysis(
  analysis_list = S.Table6_pRFcenters_Y,
  file_path = output_directory,
  file_name = "S.Table6_pRFcenters_Y",
  bold_p_value = 0.05,
  digits = 3
)

# Betas format
# output <- run_and_format_betas(
#   analysis_list = S.Table6_pRFcenters_Y,
#   file_path = output_directory,
#   file_name = "S.Table6_pRFcenters_Y",
#   bold_p_value = 0.05,
#   digits = 3
# )
```

# Supplementary Table 7. pRF Eccentricity statistics
```{r, warning=F, message=F, echo=FALSE}

S.Table7_pRFcenters_eccentricity <- list(
  list(
    data = df.centers_cat_latdors,
    formula = centerR ~ group*stream*category*hemi + (1|sub),
    filters = LMM_filters,
    analysis_name = "LMM: pRF centers Eccentricity (Age Group)"
  ),
  list(
    data = df.centers_cat_latdors,
    formula = centerR ~ group*category*hemi + (1|sub),
    filters = ventralLMM_filters,
    analysis_name = "Ventral LMM: pRF centers Eccentricity (Age Group)"
  ),
    list(
    data = df.centers_cat_latdors,
    formula = centerR ~ age*stream*category*hemi + (1|sub),
    filters = LMM_filters,
    analysis_name = "LMM: pRF centers Eccentricity (Age Continuous)"
  ),
  list(
    data = df.centers_cat_latdors,
    formula = centerR ~ age*category*hemi + (1|sub),
    filters = ventralLMM_filters,
    analysis_name = "Ventral LMM: pRF centers Eccentricity (Age Continuous)"
  )
)

# Run the function
output <- run_and_format_analysis(
  analysis_list = S.Table7_pRFcenters_eccentricity,
  file_path = output_directory,
  file_name = "S.Table7_pRFcenters_eccentricity",
  bold_p_value = 0.05,
  digits = 3
)

# Betas format
# output <- run_and_format_betas(
#   analysis_list = S.Table7_pRFcenters_eccentricity,
#   file_path = output_directory,
#   file_name = "S.Table7_pRFcenters_eccentricity",
#   bold_p_value = 0.05,
#   digits = 3
# )
```

# Supplementary Table 8. pRF size statistics
```{r, warning=F, message=F, echo=FALSE}

S.Table8_pRFcenters_size <- list(
  list(
    data = df.centers_cat_latdors,
    formula = size ~ group*stream*category*hemi + (1|sub),
    filters = LMM_filters,
    analysis_name = "LMM: pRF Size (Age Group)"
  ),
  list(
    data = df.centers_cat_latdors,
    formula = size ~ group*category*hemi + (1|sub),
    filters = ventralLMM_filters,
    analysis_name = "Ventral LMM: pRF Size (Age Group)"
  ),
    list(
    data = df.centers_cat_latdors,
    formula = size ~ age*stream*category*hemi + (1|sub),
    filters = LMM_filters,
    analysis_name = "LMM: pRF Size (Age Continuous)"
  ),
  list(
    data = df.centers_cat_latdors,
    formula = size ~ age*category*hemi + (1|sub),
    filters = ventralLMM_filters,
    analysis_name = "Ventral LMM: pRF Size (Age Continuous)"
  )
)

# Run the function
output <- run_and_format_analysis(
  analysis_list = S.Table8_pRFcenters_size,
  file_path = output_directory,
  file_name = "S.Table8_pRFcenters_size",
  bold_p_value = 0.05,
  digits = 3
)

# Betas format
# output <- run_and_format_betas(
#   analysis_list = S.Table8_pRFcenters_size,
#   file_path = output_directory,
#   file_name = "S.Table8_pRFcenters_size",
#   bold_p_value = 0.05,
#   digits = 3
# )
```

# Supplementary Table 9. FWHM statistics
```{r, warning=F, message=F, echo=FALSE}

S.Table9_FWHM <- list(
  list(
    data = df.CoV_cat_latdors,
    formula = fwhm ~ group*stream*category*hemi + (1|sub),
    filters = LMM_filters,
    analysis_name = "LMM: Total FWHM (Age Group)"
  ),
  list(
    data = df.CoV_cat_latdors,
    formula = fwhm ~ group*category*hemi + (1|sub),
    filters = ventralLMM_filters,
    analysis_name = "Ventral LMM: Total FWHM (Age Group)"
  ),
  list(
    data = df.CoV_cat_latdors,
    formula = fwhm ~ age*stream*category*hemi + (1|sub),
    filters = LMM_filters,
    analysis_name = "LMM: Total FWHM (Age Continuous)"
  ),
  list(
    data = df.CoV_cat_latdors,
    formula = fwhm ~ age*category*hemi + (1|sub),
    filters = ventralLMM_filters,
    analysis_name = "Ventral LMM: Total FWHM (Age Continuous)"
  )
)

# Run the function
output <- run_and_format_analysis(
  analysis_list = S.Table9_FWHM,
  file_path = output_directory,
  file_name = "S.Table9_FWHM",
  bold_p_value = 0.05,
  digits = 3
)

# Betas format
# output <- run_and_format_betas(
#   analysis_list = S.Table9_FWHM,
#   file_path = output_directory,
#   file_name = "S.Table9_FWHM",
#   bold_p_value = 0.05,
#   digits = 3
# )
```

# Supplementary Table 10. Category ROI size statistics + Supplementary Table 11. ROI Size betas
```{r, warning=F, message=F, echo=FALSE}

S.Table10_catSelectivity_ROIsize <- list(
  list(
    data = df.ROIsize_cat_latdors,
    formula = totalvox ~ group*stream*category*hemi + (1|sub),
    filters = LMM_filters,
    analysis_name = "LMM: ROI Size (Age Group)"
  ),
  list(
    data = df.ROIsize_cat_latdors,
    formula = totalvox ~ group*category*hemi + (1|sub),
    filters = ventralLMM_filters,
    analysis_name = "Ventral LMM: ROI Size (Age Group)"
  ),
    list(
    data = df.ROIsize_cat_latdors,
    formula = totalvox ~ age*stream*category*hemi + (1|sub),
    filters = LMM_filters,
    analysis_name = "LMM: ROI Size (Age Continuous)"
  ),
  list(
    data = df.ROIsize_cat_latdors,
    formula = totalvox ~ age*category*hemi + (1|sub),
    filters = ventralLMM_filters,
    analysis_name = "Ventral LMM: ROI Size (Age Continuous)"
  )
)

# Run the function
output <- run_and_format_analysis(
  analysis_list = S.Table10_catSelectivity_ROIsize,
  file_path = output_directory,
  file_name = "S.Table10_catSelectivity_ROIsize",
  bold_p_value = 0.05,
  digits = 3
)

#Betas format
# output <- run_and_format_betas(
#   analysis_list = S.Table10_catSelectivity_ROIsize,
#   file_path = output_directory,
#   file_name = "S.Table11_catSelectivity_ROIsize",
#   bold_p_value = 0.05,
#   digits = 3
# )
```

# Supplementart Table 11. ROI Size Emmeans Betas
```{r}

library(lme4)
library(lmerTest)
library(emmeans)
library(dplyr)
library(gt)
library(stringr)

#---------------------------------------------------------
# Function to run an LMM, extract betas, format nicely
#---------------------------------------------------------
extract_betas <- function(data, model_formula, analysis_label) {
  
  # 1. Run model
  emm_obj <- data %>%
    lmer(model_formula, .) %>%
    emmeans(~ group | category)
  
  # 2. Adult - adolescent pairwise comparisons
  betas <- pairs(emm_obj, by = "category", reverse = TRUE) %>%
    as.data.frame() %>%
    mutate(
      Analysis = analysis_label,
      estimate = round(estimate, 3),
      SE = round(SE, 3),
      df = round(df, 1),
      t.ratio = round(t.ratio, 3),
      p.value = ifelse(p.value < 0.0001,
                       format(p.value, scientific = TRUE, digits = 3),
                       format(round(p.value, 3), nsmall = 3)),
      Sig = ifelse(p.value < 0.05, "*", "")
    )
  
  return(betas)
}

#---------------------------------------------------------
# Run BOTH analyses
#---------------------------------------------------------

# Analysis 1 dataset: ventral + dorsal-lateral (minus word ROIs)
analysis1_data <- df.ROIsize_cat_latdors

analysis1 <- extract_betas(
  data = analysis1_data,
  model_formula = totalvox ~ group * category * stream * hemi + (1|sub),
  analysis_label = "LMM (no words)"
)

# Analysis 2 dataset: ventral only
analysis2_data <- df.ROIsize_cat_latdors %>% filter(stream == "ventral")# <-- you must define this dataset

analysis2 <- extract_betas(
  data = analysis2_data,
  model_formula = totalvox ~ group * category * hemi + (1|sub),
  analysis_label = "Ventral LMM"
)

#---------------------------------------------------------
# Combine both sets of betas into ONE clean table
#---------------------------------------------------------

all_betas <- bind_rows(analysis1, analysis2)

# Order fields in logical layout
all_betas <- all_betas %>%
  select(
    Analysis, category, contrast, estimate, SE, df, t.ratio, p.value, Sig
  )

library(knitr)
library(kableExtra)
library(dplyr)

# ---- format columns like your other tables ----
betas_out <- all_betas %>%
  mutate(
    estimate = formatC(as.numeric(estimate), format = "f", digits = 3),
    SE       = formatC(as.numeric(SE),       format = "f", digits = 3),
    df       = formatC(as.numeric(df),       format = "f", digits = 1),
    t.ratio  = formatC(as.numeric(t.ratio),  format = "f", digits = 3),
    # keep your p.value string as-is (already formatted)
    Sig      = ifelse(Sig == "*", "*", "")
  ) %>%
  select(Analysis, category, contrast, estimate, SE, df, t.ratio, p.value, Sig) %>%
  group_by(Analysis) %>%
  mutate(Analysis = ifelse(row_number() == 1, Analysis, "")) %>%  # match your “Analysis once” style
  ungroup()

# ---- add blank spacer row between analyses (matches your other tables) ----
starts <- which(betas_out$Analysis != "")
if (length(starts) > 1) {
  spacer <- as.list(rep("", ncol(betas_out)))
  names(spacer) <- names(betas_out)

  for (i in rev(starts[-1])) {
    betas_out <- bind_rows(
      betas_out[1:(i-1), ],
      spacer,
      betas_out[i:nrow(betas_out), ]
    )
  }
}

# ---- build LaTeX table in the SAME style as your other kable tables ----
kbl <- betas_out %>%
  kable(
    format = "latex",
    booktabs = TRUE,
    longtable = TRUE,
    escape = FALSE,  # allows β if you want LaTeX symbols later
    col.names = c("Analysis", "Category", "Group Contrast", "$\\beta$", "SE", "df", "t", "p-value", "")
  ) %>%
  kable_styling(latex_options = c("hold_position"))

# ---- bold significant rows (where Sig == "*") ----
sig_rows <- which(betas_out$Sig == "*")
if (length(sig_rows) > 0) {
  for (r in sig_rows) kbl <- row_spec(kbl, r, bold = TRUE)
}

# ---- save .tex (matching your other outputs) ----
save_kable(
  kbl,
  file = file.path(output_directory, "S.Table11_All_LMM_ROIsize_emm_betas.tex")
)

```

# Supplementary Table 12. Category selectivity statistics
```{r, warning=F, message=F, echo=FALSE}

S.Table12_catSelectivity_meanT <- list(
  list(
    data = df.category_latdors,
    formula = meanT ~ group*stream*category*hemi + (1|sub),
    filters = LMM_filters,
    analysis_name = "LMM: Category Selectivity - Mean T-Value (Age Group)"
  ),
  list(
    data = df.category_latdors,
    formula = meanT ~ group*category*hemi + (1|sub),
    filters = ventralLMM_filters,
    analysis_name = "Ventral LMM: Category Selectivity - Mean T-Value  (Age Group)"
  ),
    list(
    data = df.category_latdors,
    formula = meanT ~ age*stream*category*hemi + (1|sub),
    filters = LMM_filters,
    analysis_name = "LMM: Category Selectivity - Mean T-Value  (Age Continuous)"
  ),
  list(
    data = df.category_latdors,
    formula = meanT ~ age*category*hemi + (1|sub),
    filters = ventralLMM_filters,
    analysis_name = "Ventral LMM: Category Selectivity - Mean T-Value  (Age Continuous)"
  )
)

# Run the function
output <- run_and_format_analysis(
  analysis_list = S.Table12_catSelectivity_meanT,
  file_path = output_directory,
  file_name = "S.Table12_catSelectivity_meanT",
  bold_p_value = 0.05,
  digits = 3
)

# Betas format
# output <- run_and_format_betas(
#   analysis_list = S.Table11_catSelectivity_meanT,
#   file_path = output_directory,
#   file_name = "S.Table11_catSelectivity_meanT",
#   bold_p_value = 0.05,
#   digits = 3
# )

```


# Supplementary Table 13. Category selectivity vs Spatial Integration + Supplementary Table 14. Betas
```{r, warning=F, message=F, echo=FALSE}

S.Table13_catSelectVspatialInteg<- list(
  list(
    data = df.new_analysis,
    formula = totalvox ~ fwhm + size + ecc + group + (1|sub),
    filters = LMM_filters,
    analysis_name = "LMM: ROI size ~ fwhm + size + ecc + group"
  ),
  list(
    data = df.new_analysis,
    formula = meanT ~ fwhm + size + ecc + group + (1|sub),
    filters = LMM_filters,
    analysis_name = "LMM: meanT ~ fwhm + size + ecc + group"
  )
)

# Run the function
output <- run_and_format_analysis(
  analysis_list = S.Table13_catSelectVspatialInteg,
  file_path = output_directory,
  file_name = "S.Table13_catSelectVspatialInteg",
  bold_p_value = 0.05,
  digits = 3
)

# Betas format
output <- run_and_format_betas(
  analysis_list = S.Table13_catSelectVspatialInteg,
  file_path = output_directory,
  file_name = "S.Table14_catSelectVspatialInteg",
  bold_p_value = 0.05,
  digits = 3
)
```

```{r}
old_wd <- getwd()
setwd(output_directory)

system('for f in *.tex; do pandoc "$f" --reference-doc=reference.docx -o "${f%.tex}.docx"; done')

setwd(old_wd)

```

