---
title: "toonCat_postHoc_ttests"
author: "Jewelia K. Yao"
date: "`r Sys.Date()`"
output: html_document
---

TOONCAT POST-HOC ANALYSES
Post-hoc t-tests conducted for the toonCat manuscript. Each post-hoc t-test compares age groups (adolescents, adults)for each hemisphere-ROI region. Post-hoc testing was conducted for any LMM that showed significant age group effects or age group interaction effects.

# Setup
```{r Setup, warning=F, message=F, echo=FALSE}
# Setup file
setwd("~/Desktop/toonCat/analysis")
source("~/Desktop/toonCat/analysis/code/toonCat_analysisSetup.R")
```

# Post-Hoc T-Test Function: splitting df, performing t-tests, extracting parameters, saving table
```{r}
perform_and_save_t_tests <- function(data, split_var, group_var, measure_var, output_file) {
  # Splitting by hemisphere and ROI
  data_filtered <- data %>%
    filter(hemi %in% c("lh", "rh"), !(ROI %in% c("blank", "blank1", "blank2", "blank3", "blank4"))) %>%
    na.omit()
  split_data <- split(data_filtered, list(data_filtered$hemi, data_filtered$ROI))

  # Function to perform t-test and return parameters
  perform_t_test <- function(data) {
    group_data <- data %>% filter(group == "adolescents") %>% pull(!!sym(measure_var))
    adult_data <- data %>% filter(group == "Adults") %>% pull(!!sym(measure_var))
    if (length(group_data) > 0 & length(adult_data) > 0) {
      t_test_result <- t.test(group_data, adult_data, var.equal = FALSE)
      return(tibble(
        hemi = unique(data$hemi),
        ROI = unique(data$ROI),
        t_statistic = t_test_result$statistic,
        p_value = t_test_result$p.value,
        df = t_test_result$parameter,
        mean_adolescents = mean(group_data, na.rm = TRUE),
        mean_Adults = mean(adult_data, na.rm = TRUE)
      ))
    } else {
      return(NULL)
    }
  }

  # Applying t-test function to each split dataframe and combining results into a single table
  t_test_results <- bind_rows(lapply(split_data, perform_t_test))

  # Displaying and saving the results
  t_test_results %>%
    kable(format = 'html', padding = '1L', booktabs = TRUE, linesep = "\\addlinespace", digits = 10) %>%
    kable_styling(full_width = FALSE) %>%
    row_spec(which(as.numeric(t_test_results$p_value) < 0.05), bold = TRUE) %>%
    save_kable(file = output_file)
  
  print(t_test_results)
}
```

# pRF Size
```{r}
# Example usage
perform_and_save_t_tests(df.centers_cat_latdors, "size", "group", "size", "~/Desktop/toonCat/analysis/figures_tables/posthoc/pRFsize_t_test_unequalVariance.png")
```

# Total FWHM
```{r}
perform_and_save_t_tests(df.CoV_cat_latdors, "fwhm", "group", "fwhm", "~/Desktop/toonCat/analysis//figures_tables/posthoc/CoV_totalFWHM_t_test_unequalVariance.png")
```

# Category Selectivity
```{r}
perform_and_save_t_tests(df.cat, "meanT", "group", "meanT", "~/Desktop/toonCat/analysis/figures_tables/posthoc/catSelectivity_t_test_unequalVariance_10mm.png")
```

# ROI Size
```{r}
perform_and_save_t_tests(df.ROIsize_cat_latdors, "totalvox", "group", "totalvox", "~/Desktop/toonCat/analysis/figures_tables/posthoc/ROIsize_t-tests.png")
```

