---
title: "toonCat_supplementaryFiguresTables"
author: "Jewelia K. Yao"
date: '`r Sys.Date()`'
output: html_document
---

TOONCAT SUPPLEMENTARY FIGURES AND TABLES
Supplementary tables and figures, in order of reference, for the toonCat manuscript. Includes only the R generated plots, but other figures are noted. See MATLAB scripts and figures folder for other figure components. Supplement includes all main statistics computed in the manuscript.

```{r Setup, warning=F, message=F, echo=FALSE}
# Setup file
source("~/Desktop/FYP/toonCat/results/toonCat_analysisSetup.R")

# Set global variables
output_directory <- "~/Desktop/FYP/toonCat/results/figures_tables/supplementary/tables"
LMM_filters <- c("hemi != 'mh'", "hemi != 'zh'", "ROI != 'blank'","ROI != 'blank1'", "category != 'word'", "category != 'words'")
ventralLMM_filters <- c("hemi != 'mh'", "hemi != 'zh'", "ROI != 'blank'","ROI != 'blank1'", "stream == 'ventral'")
retinotopyLMM_filters <- c("ROI %in% c('V1', 'V2', 'V3')", "hemi != 'mh'", "hemi != 'zh'")
```

# FUNCTIONS
```{r}
run_and_format_analysis <- function(analysis_list, file_path, file_name, bold_p_value = 0.05, digits = 3) {
  
  # Helper function to process individual analyses
  run_LMM_analysis <- function(data, formula, filters = NULL, analysis_name) {
  # Apply filters dynamically if provided
  if (!is.null(filters) && length(filters) > 0) {
    filtered_data <- data %>%
      filter(!!!rlang::parse_exprs(filters)) %>%
      na.omit()
  } else {
    filtered_data <- data %>%
      na.omit()
  }
  
  # Fit the model and perform joint tests
  model <- lmer(formula, data = filtered_data)
  results <- joint_tests(model)
  
  # Add the analysis name as a column
  results <- results %>%
    mutate(Analysis = analysis_name)
  
  return(results)
}

  
  # Process each analysis
  combined_results <- bind_rows(lapply(analysis_list, function(analysis) {
    run_LMM_analysis(
      data = analysis$data,
      formula = analysis$formula,
      filters = analysis$filters,
      analysis_name = analysis$analysis_name
    )
  }))
  
  # Define the format and save function
  format_and_save_table <- function(results, file_path, bold_p = TRUE, bold_p_value, digits) {
    # Format p-values and F-ratios
    format_p <- function(p) {
      ifelse(p < 0.0001, format(p, scientific = TRUE, digits = 4), format(p, nsmall = 3))
    }
    format_F <- function(Fval) {
      format(Fval, nsmall = digits)
    }
    
    # Reorder columns to make "Analysis" the first column
    formatted_results <- results %>%
      mutate(
        p.value = as.numeric(p.value),
        p.value = sapply(p.value, format_p),
        F.ratio = sapply(F.ratio, format_F)
      ) %>%
      select(Analysis, everything()) %>%  # Ensure Analysis is the first column
      group_by(Analysis) %>%
      mutate(Analysis = ifelse(row_number() == 1, Analysis, "")) %>%  # Show Analysis name only in the first row
      ungroup()
    
    # Identify the rows where a new analysis starts (first row of each analysis group)
    add_space_rows <- which(formatted_results$Analysis != "")
    
    # Generate the table
    table <- formatted_results %>%
      kable(format = "html", booktabs = TRUE, digits = digits) %>%
      kable_classic(full_width = FALSE, html_font = "Calibri")
    
    # Add spacing above rows where a new analysis starts (excluding the first analysis)
    for (row in add_space_rows[-1]) {  # Skip the first analysis row
      table <- table %>%
        row_spec(row, extra_css = "border-top: 10px solid white;")
    }
    
    # Apply bolding conditionally based on `bold_p`
    if (bold_p) {
      table <- table %>%
        row_spec(which(as.numeric(formatted_results$p.value) < bold_p_value), bold = TRUE)
    }
    
    # Save the table
    save_kable(table, file = file_path, zoom = 3, density = 500)
    
    return(formatted_results)  # Return the formatted results in case further use is needed
  }
  
  # Construct full file paths
  bold_file_path <- file.path(file_path, paste0(file_name, "_bold.png"))
  no_bold_file_path <- file.path(file_path, paste0(file_name, ".png"))
  
  # Save bolded table
  formatted_results_bold <- format_and_save_table(
    results = combined_results,
    file_path = bold_file_path,
    bold_p = TRUE,
    bold_p_value = bold_p_value,
    digits = digits
  )
  
  # Save non-bolded table
  formatted_results_no_bold <- format_and_save_table(
    results = combined_results,
    file_path = no_bold_file_path,
    bold_p = FALSE,
    bold_p_value = bold_p_value,
    digits = digits
  )
  
  # Return combined results and paths to saved files
  return(list(
    combined_results = combined_results,
    bold_output_file = bold_file_path,
    no_bold_output_file = no_bold_file_path
  ))
}
```

```{r}
run_and_format_analysis_asCSV <- function(analysis_list, file_path, file_name, bold_p_value = 0.05, digits = 3) {
  
  # Helper function to process individual analyses
  run_LMM_analysis <- function(data, formula, filters = NULL, analysis_name) {
    if (!is.null(filters) && length(filters) > 0) {
      filtered_data <- data %>%
        filter(!!!rlang::parse_exprs(filters)) %>%
        na.omit()
    } else {
      filtered_data <- data %>%
        na.omit()
    }
    
    model <- lmer(formula, data = filtered_data)
    results <- joint_tests(model)
    
    # Add the analysis name as a column
    results <- results %>%
      mutate(Analysis = analysis_name)
    
    return(results)
  }

  # Process each analysis
  combined_results <- bind_rows(lapply(analysis_list, function(analysis) {
    run_LMM_analysis(
      data = analysis$data,
      formula = analysis$formula,
      filters = analysis$filters,
      analysis_name = analysis$analysis_name
    )
  }))

  # Ensure the Analysis column is the first
  combined_results <- combined_results %>%
    dplyr::select(Analysis, everything())

  # Save the results to CSV
  results_path <- file.path(file_path, paste0(file_name, ".csv"))
  write.csv(combined_results, file = results_path, row.names = FALSE)

  # Return combined results and path to saved file
  return(list(
    combined_results = combined_results,
    output_file = results_path
  ))
}
```


# Supplementary Figure 1. Phase maps for all participants
See figure folder

# Supplementary Figure 2. Eccentricity maps for all participants
See figure folder

# Supplementary Figure 3. Size maps for all participants
See figure folder

# Supplementary Table 1. V1, V2, V3 statistics
```{r, warning=F, message=F, echo=FALSE}
S.Table1_V1V2V3 <- list(
  list(
    data = df.centers,
    formula = centerX ~ group*ROI*hemi + (1|sub),
    filters = retinotopyLMM_filters,
    analysis_name = "LMM: pRF centers X-position (Age Group)"
  ),
    list(
    data = df.centers,
    formula = centerY ~ group*ROI*hemi + (1|sub),
    filters = retinotopyLMM_filters,
    analysis_name = "LMM: pRF centers Y-position (Age Group)"
  ),
    list(
    data = df.centers,
    formula = centerR ~ group*ROI*hemi + (1|sub),
    filters = retinotopyLMM_filters,
    analysis_name = "LMM: pRF centers Eccentricity (Age Group)"
  ),
    list(
    data = df.centers,
    formula = size ~ group*ROI*hemi + (1|sub),
    filters = retinotopyLMM_filters,
    analysis_name = "LMM: pRF size (Age Group)"
  )
)

# Run the function
output <- run_and_format_analysis(
  analysis_list = S.Table1_V1V2V3,
  file_path = output_directory,
  file_name = "S.Table1_V1V2V3",
  bold_p_value = 0.05,
  digits = 3
)

# CSV format
output <- run_and_format_analysis_asCSV(
  analysis_list = S.Table1_V1V2V3,
  file_path = output_directory,
  file_name = "S.Table1_V1V2V3",
  bold_p_value = 0.05,
  digits = 3
)
```

# Supplementary Table 2. pRF size vs eccentricity statistics
```{r, warning=F, message=F, echo=FALSE}

S.Table2_sizeVecc <- list(
  list(
    data = df.sizeEcc_ret,
    formula = slope ~ group*ROI*hemi + (1|sub),
    filters = NULL,
    analysis_name = "LMM: Size v. Ecc Slopes"
  ),
  list(
    data = df.sizeEcc_ret,
    formula = intercept ~ group*ROI*hemi + (1|sub),
    filters = NULL,
    analysis_name = "LMM: Size v. Ecc Intercepts"
  )
)

# Run the function
output <- run_and_format_analysis(
  analysis_list = S.Table2_sizeVecc,
  file_path = output_directory,
  file_name = "S.Table2_sizeVecc_slopes_intercepts",
  bold_p_value = 0.05,
  digits = 3
)

# CSV format
output <- run_and_format_analysis_asCSV(
  analysis_list = S.Table2_sizeVecc,
  file_path = output_directory,
  file_name = "S.Table2_sizeVecc_slopes_intercepts",
  bold_p_value = 0.05,
  digits = 3
)
```

# Supplementary Table 3. Number of individuals with ROI per group
```{r}
# Create summary table
summary_table <- df.CoV_cat_latdors %>%
  na.omit() %>%
  filter(hemi %in% c("lh", "rh")) %>%
  group_by(ROI, hemi, group) %>%
  summarise(N = n_distinct(subject), .groups = "drop") %>%
  pivot_wider(
    names_from = c(group, hemi), 
    values_from = N) %>%
  mutate(ROI = stringr::str_replace_all(ROI, "_", "-"),
         ROI = stringr::str_replace_all(ROI, "limbs", "bodies"),
         adolescents_rh = ifelse(ROI == "mOTS-words", " ", adolescents_rh),
         Adults_rh = ifelse(ROI == "mOTS-words", " ", Adults_rh),
         ROI = ifelse(ROI == "pSTS-faces", "pSTS-faces*", ROI),
         ROI = ifelse(ROI == "MTG-bodies", "MTG-bodies*", ROI))

# Define headers with subcolumns for hemispheres under each measure
measure_headers <- c(
  " " = 1, "Left Hemisphere" = 2, "Right Hemisphere" = 2)

# Manually set column names
colnames(summary_table) <- c(
  "ROI", "adolescents", "Adults", "adolescents", "Adults")

# Create HTML tables
count_table <- summary_table %>%
  kbl(caption = "",  align=('lcccc')) %>%
  kable_classic(full_width = F, html_font = "Calibri") %>%
  row_spec(7, extra_css = "padding-bottom: 30px;") %>% 
  row_spec(11, extra_css = "padding-bottom: 30px;") %>%
  add_header_above(measure_headers, extra_css = "font-size: 10px;") %>%
 save_kable(file = file.path(output_directory, "S.Table3_ROI_counts.png"),
            zoom = 3, 
            density = 500)

# Save the table to a CSV file
csv_path <- file.path(output_directory, "S.Table3_ROI_counts.csv")
write.csv(summary_table, file = csv_path, row.names = FALSE)
```

# Supplementary Table 4. Proportion of voxels with VE > 20% statistics
```{r, warning=F, message=F, echo=FALSE}

S.Table4_proportionVE20 <- list(
  list(
    data = df.CoV_cat_latdors,
    formula = proportion20 ~ group*stream*category*hemi + (1|sub),
    filters = LMM_filters,
    analysis_name = "LMM: Proportion Voxels with Variance Explained > 20%"
  ),
  list(
    data = df.CoV_cat_latdors,
    formula = proportion20 ~ group*category*hemi + (1|sub),
    filters = ventralLMM_filters,
    analysis_name = "Ventral LMM: Proportion Voxels with Variance Explained > 20%"
  )
)

# Run the function
output <- run_and_format_analysis(
  analysis_list = S.Table4_proportionVE20,
  file_path = output_directory,
  file_name = "S.Table4_proportionVE20",
  bold_p_value = 0.05,
  digits = 3
)

# CSV format
output <- run_and_format_analysis_asCSV(
  analysis_list = S.Table4_proportionVE20,
  file_path = output_directory,
  file_name = "S.Table4_proportionVE20",
  bold_p_value = 0.05,
  digits = 3
)
```

# Supplementary Figure 4. pRF x-position
```{r pRF x-position, fig.width=12, fig.height=4, warning=F, message=F, echo=FALSE}
png(file.path(output_directory, "S.F4_pRFcenters_xPosition_violin.png"), units="in", width=15, height=2.25, res=300)
df.centers_cat %>%
  ggplot(., aes(x = interaction(group, hemi, sep = "."), 
                y = centerX, 
                color = ROI, 
                fill = ROI, 
                alpha = hemi)) +
  geom_violin(position = position_dodge(width = 0.8), na.rm = TRUE) + 
  geom_point(size = 0.5, na.rm = TRUE) +
  stat_summary(fun.y = mean,
               geom = "pointrange", 
               color = "black") +
  stat_summary(fun.data = mean_se, 
               geom = "errorbar", 
               color = "black") +
  geom_hline(yintercept = 0) +
  labs(y = "X Position  (°)") +
  facet_grid(~ ROI) +
  theme(legend.position = "none",
        strip.background = element_blank(),
        strip.text.x = element_blank(),
        axis.title.y=element_text(size=16),
        panel.spacing = unit(0, "null"),
        panel.grid.major.y = element_line(color = "gray96",size = 0.5),
        axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.text.y = element_text(size = 15),
        text = element_text(family = "Avenir")) +
  scale_color_manual(values = roi_colors, na.translate = FALSE) +
  scale_alpha_manual(values = c("lh" = 0.45, "rh" = 0.8)) +
  scale_fill_manual(values = roi_colors, na.translate = FALSE) +
  scale_y_continuous(breaks = seq(-20, 20, 5), limits = c(-21, 21)) 
dev.off()
```

# Supplementary Table 5. pRF x-position statistics
```{r, warning=F, message=F, echo=FALSE}

S.Table5_pRFcenters_X <- list(
  list(
    data = df.centers_cat_latdors,
    formula = centerX ~ group*stream*category*hemi + (1|sub),
    filters = LMM_filters,
    analysis_name = "LMM: pRF centers X-position (Age Group)"
  ),
  list(
    data = df.centers_cat_latdors,
    formula = centerX ~ group*category*hemi + (1|sub),
    filters = ventralLMM_filters,
    analysis_name = "Ventral LMM: pRF centers X-position (Age Group)"
  ),
    list(
    data = df.centers_cat_latdors,
    formula = centerX ~ age*stream*category*hemi + (1|sub),
    filters = LMM_filters,
    analysis_name = "LMM: pRF centers X-position (Age Continuous)"
  ),
  list(
    data = df.centers_cat_latdors,
    formula = centerX ~ age*category*hemi + (1|sub),
    filters = ventralLMM_filters,
    analysis_name = "Ventral LMM: pRF centers X-position (Age Continuous)"
  )
)

# Run the function
output <- run_and_format_analysis(
  analysis_list = S.Table5_pRFcenters_X,
  file_path = output_directory,
  file_name = "S.Table5_pRFcenters_X",
  bold_p_value = 0.05,
  digits = 3
)

# CSV format
output <- run_and_format_analysis_asCSV(
  analysis_list = S.Table5_pRFcenters_X,
  file_path = output_directory,
  file_name = "S.Table5_pRFcenters_X",
  bold_p_value = 0.05,
  digits = 3
)
```

# Supplementary Table 6. pRF y-position statistics
```{r, warning=F, message=F, echo=FALSE}

S.Table6_pRFcenters_Y <- list(
  list(
    data = df.centers_cat_latdors,
    formula = centerY ~ group*stream*category*hemi + (1|sub),
    filters = LMM_filters,
    analysis_name = "LMM: pRF centers Y-position (Age Group)"
  ),
  list(
    data = df.centers_cat_latdors,
    formula = centerY ~ group*category*hemi + (1|sub),
    filters = ventralLMM_filters,
    analysis_name = "Ventral LMM: pRF centers Y-position (Age Group)"
  ),
    list(
    data = df.centers_cat_latdors,
    formula = centerY ~ age*stream*category*hemi + (1|sub),
    filters = LMM_filters,
    analysis_name = "LMM: pRF centers Y-position (Age Continuous)"
  ),
  list(
    data = df.centers_cat_latdors,
    formula = centerY ~ age*category*hemi + (1|sub),
    filters = ventralLMM_filters,
    analysis_name = "Ventral LMM: pRF centers Y-position (Age Continuous)"
  )
)

# Run the function
output <- run_and_format_analysis(
  analysis_list = S.Table6_pRFcenters_Y,
  file_path = output_directory,
  file_name = "S.Table6_pRFcenters_Y",
  bold_p_value = 0.05,
  digits = 3
)

# CSV format
output <- run_and_format_analysis_asCSV(
  analysis_list = S.Table6_pRFcenters_Y,
  file_path = output_directory,
  file_name = "S.Table6_pRFcenters_Y",
  bold_p_value = 0.05,
  digits = 3
)
```

# Supplementary Table 7. pRF Eccentricity statistics
```{r, warning=F, message=F, echo=FALSE}

S.Table7_pRFcenters_eccentricity <- list(
  list(
    data = df.centers_cat_latdors,
    formula = centerR ~ group*stream*category*hemi + (1|sub),
    filters = LMM_filters,
    analysis_name = "LMM: pRF centers Eccentricity (Age Group)"
  ),
  list(
    data = df.centers_cat_latdors,
    formula = centerR ~ group*category*hemi + (1|sub),
    filters = ventralLMM_filters,
    analysis_name = "Ventral LMM: pRF centers Eccentricity (Age Group)"
  ),
    list(
    data = df.centers_cat_latdors,
    formula = centerR ~ age*stream*category*hemi + (1|sub),
    filters = LMM_filters,
    analysis_name = "LMM: pRF centers Eccentricity (Age Continuous)"
  ),
  list(
    data = df.centers_cat_latdors,
    formula = centerR ~ age*category*hemi + (1|sub),
    filters = ventralLMM_filters,
    analysis_name = "Ventral LMM: pRF centers Eccentricity (Age Continuous)"
  )
)

# Run the function
output <- run_and_format_analysis(
  analysis_list = S.Table7_pRFcenters_eccentricity,
  file_path = output_directory,
  file_name = "S.Table7_pRFcenters_eccentricity",
  bold_p_value = 0.05,
  digits = 3
)

# CSV format
output <- run_and_format_analysis_asCSV(
  analysis_list = S.Table7_pRFcenters_eccentricity,
  file_path = output_directory,
  file_name = "S.Table7_pRFcenters_eccentricity",
  bold_p_value = 0.05,
  digits = 3
)
```

# Supplementary Table 8. pRF size statistics
```{r, warning=F, message=F, echo=FALSE}

S.Table8_pRFcenters_size <- list(
  list(
    data = df.centers_cat_latdors,
    formula = size ~ group*stream*category*hemi + (1|sub),
    filters = LMM_filters,
    analysis_name = "LMM: pRF Size (Age Group)"
  ),
  list(
    data = df.centers_cat_latdors,
    formula = size ~ group*category*hemi + (1|sub),
    filters = ventralLMM_filters,
    analysis_name = "Ventral LMM: pRF Size (Age Group)"
  ),
    list(
    data = df.centers_cat_latdors,
    formula = size ~ age*stream*category*hemi + (1|sub),
    filters = LMM_filters,
    analysis_name = "LMM: pRF Size (Age Continuous)"
  ),
  list(
    data = df.centers_cat_latdors,
    formula = size ~ age*category*hemi + (1|sub),
    filters = ventralLMM_filters,
    analysis_name = "Ventral LMM: pRF Size (Age Continuous)"
  )
)

# Run the function
output <- run_and_format_analysis(
  analysis_list = S.Table8_pRFcenters_size,
  file_path = output_directory,
  file_name = "S.Table8_pRFcenters_size",
  bold_p_value = 0.05,
  digits = 3
)

# CSV format
output <- run_and_format_analysis_asCSV(
  analysis_list = S.Table8_pRFcenters_size,
  file_path = output_directory,
  file_name = "S.Table8_pRFcenters_size",
  bold_p_value = 0.05,
  digits = 3
)
```

# Supplementary Table 9. FWHM statistics
```{r, warning=F, message=F, echo=FALSE}

S.Table9_FWHM <- list(
  list(
    data = df.CoV_cat_latdors,
    formula = fwhm ~ group*stream*category*hemi + (1|sub),
    filters = LMM_filters,
    analysis_name = "LMM: Total FWHM (Age Group)"
  ),
  list(
    data = df.CoV_cat_latdors,
    formula = fwhm ~ group*category*hemi + (1|sub),
    filters = ventralLMM_filters,
    analysis_name = "Ventral LMM: Total FWHM (Age Group)"
  ),
  list(
    data = df.CoV_cat_latdors,
    formula = fwhm ~ group*stream*category*hemi + (1|sub),
    filters = LMM_filters,
    analysis_name = "LMM: Total FWHM (Age Continuous)"
  ),
  list(
    data = df.CoV_cat_latdors,
    formula = fwhm ~ group*category*hemi + (1|sub),
    filters = ventralLMM_filters,
    analysis_name = "Ventral LMM: Total FWHM (Age Continuous)"
  )
)

# Run the function
output <- run_and_format_analysis(
  analysis_list = S.Table9_FWHM,
  file_path = output_directory,
  file_name = "S.Table9_FWHM",
  bold_p_value = 0.05,
  digits = 3
)

# CSV format
output <- run_and_format_analysis_asCSV(
  analysis_list = S.Table9_FWHM,
  file_path = output_directory,
  file_name = "S.Table9_FWHM",
  bold_p_value = 0.05,
  digits = 3
)
```

# Supplementary Table 10. FWHM Quadrant Percentages
``` {r}
CoV_table <- df.CoV_cat %>%
  mutate(group = recode(group, "kids" = "adolescents")) %>%
  group_by(ROI, hemi, group) %>%
  na.omit() %>%
  summarise(
    mean_upperContra = mean(fwhm_upperContra, na.rm = TRUE),
    sd_upperContra = sd(fwhm_upperContra, na.rm = TRUE),
    mean_lowerContra = mean(fwhm_lowerContra, na.rm = TRUE),
    sd_lowerContra = sd(fwhm_lowerContra, na.rm = TRUE),
    mean_upperIpsi = mean(fwhm_upperIpsi, na.rm = TRUE),
    sd_upperIpsi = sd(fwhm_upperIpsi, na.rm = TRUE),
    mean_lowerIpsi = mean(fwhm_lowerIpsi, na.rm = TRUE),
    sd_lowerIpsi = sd(fwhm_lowerIpsi, na.rm = TRUE),
    mean_central5 = mean(fwhm_central5, na.rm = TRUE),
    sd_central5 = sd(fwhm_central5, na.rm = TRUE)
  ) %>%
  mutate(
      UC = as.character(paste0(format(round(mean_upperContra, 0), nsmall = 0), " ± ", format(round(sd_upperContra, 0), nsmall = 0))),
    LC = as.character(paste0(format(round(mean_lowerContra, 0), nsmall = 0), " ± ", format(round(sd_lowerContra, 0), nsmall = 0))),
    UI = as.character(paste0(format(round(mean_upperIpsi, 0), nsmall = 0), " ± ", format(round(sd_upperIpsi, 0), nsmall = 0))),
    LI = as.character(paste0(format(round(mean_lowerIpsi, 0), nsmall = 0), " ± ", format(round(sd_lowerIpsi, 0), nsmall = 0))),
    central5 = as.character(paste0(format(round(mean_central5, 0), nsmall = 0), " ± ", format(round(sd_central5, 0), nsmall = 0)))
  ) %>%
  na.omit() %>%
  select(ROI, hemi, group, UC, LC, UI, LI, central5)

# Pivot the table to restructure it for the desired layout
CoV_table_transformed <- CoV_table %>%
  pivot_longer(
    cols = UC:central5, # Select all measure columns
    names_to = "Measure", 
    values_to = "Value"
  ) %>%
  pivot_wider(
    names_from = c(Measure, hemi), # Create subheadings for measures and hemispheres
    values_from = Value
  )%>%
  mutate(
    UC_rh= ifelse(ROI == "mOTS_words", " ", UC_rh),
    UI_rh = ifelse(ROI == "mOTS_words", " ", UI_rh),
    LC_rh = ifelse(ROI == "mOTS_words", " ", LC_rh),
    LI_rh = ifelse(ROI == "mOTS_words", " ", LI_rh),
    central5_rh = ifelse(ROI == "mOTS_words", " ", central5_rh),
    ROI = stringr::str_replace_all(ROI, "_", "-") # Replace underscores with hyphens
  ) %>%
  select(ROI, group, UC_lh, UC_rh, LC_lh, LC_rh, LI_lh, LI_rh, UI_lh, UI_rh, central5_lh,central5_rh) 

# Save the transformed table to a CSV file
csv_path <- file.path(output_directory,"S.Table10_VFC_FWHM_Quadrant_percentages.csv")
write.csv(CoV_table_transformed, file = csv_path, row.names = FALSE)

# Print message to confirm saving
print(paste("CSV Table saved to:", csv_path))

# Define headers with subcolumns for hemispheres under each measure
measure_headers <- c(
  " " = 2, "UC" = 2, "LC" = 2, "LI" = 2, "UI" = 2, "<5°" = 2) # Repeat each measure for hemispheres

# Manually set column names
colnames(CoV_table_transformed) <- c(
  "ROI", "Group", 
  "lh", "rh", "lh", "rh", "lh", "rh", "lh", "rh", 
   "lh", "rh")


# Create the kable table with headers and subheaders
CoV_table_transformed %>%
  kable("html", booktabs = TRUE, linesep = " ") %>%
  kable_styling(
    full_width = TRUE, 
    position = "center", 
    font_size = 16
  ) %>%
  add_header_above(measure_headers, extra_css = "font-size: 20px;") %>%
  # Manual column padding
  column_spec(1, extra_css = "min-width: 80px; white-space: nowrap; padding-left: 10px; padding-right: 10px; font-size: 16px;") %>%  
  column_spec(3:9, extra_css = "min-width: 80px; white-space: nowrap; padding-left: 10px; padding-right: 10px; font-size: 16px;") %>%  
  column_spec(10, extra_css = "min-width: 80px; white-space: nowrap; padding-left: 10px; padding-right: 40px;font-size: 16px;") %>%
 column_spec(11:12, extra_css = "min-width: 80px; white-space: nowrap; padding-left: 10px; padding-right: 10px;font-size: 16px;") %>%
  save_kable(file = file.path(output_directory, "S.Table10_VFC_FWHM_Quadrant_percentages.png"))
```

# Supplementary Table 11. Category selectivity statistics
```{r, warning=F, message=F, echo=FALSE}

S.Table11_catSelectivity_meanT <- list(
  list(
    data = df.category_latdors,
    formula = meanT ~ group*stream*category*hemi + (1|sub),
    filters = LMM_filters,
    analysis_name = "LMM: Category Selectivity - Mean T-Value (Age Group)"
  ),
  list(
    data = df.category_latdors,
    formula = meanT ~ group*category*hemi + (1|sub),
    filters = ventralLMM_filters,
    analysis_name = "Ventral LMM: Category Selectivity - Mean T-Value  (Age Group)"
  ),
    list(
    data = df.category_latdors,
    formula = meanT ~ age*stream*category*hemi + (1|sub),
    filters = LMM_filters,
    analysis_name = "LMM: Category Selectivity - Mean T-Value  (Age Continuous)"
  ),
  list(
    data = df.category_latdors,
    formula = meanT ~ age*category*hemi + (1|sub),
    filters = ventralLMM_filters,
    analysis_name = "Ventral LMM: Category Selectivity - Mean T-Value  (Age Continuous)"
  )
)

# Run the function
output <- run_and_format_analysis(
  analysis_list = S.Table11_catSelectivity_meanT,
  file_path = output_directory,
  file_name = "S.Table11_catSelectivity_meanT",
  bold_p_value = 0.05,
  digits = 3
)

# CSV format
output <- run_and_format_analysis_asCSV(
  analysis_list = S.Table11_catSelectivity_meanT,
  file_path = output_directory,
  file_name = "S.Table11_catSelectivity_meanT",
  bold_p_value = 0.05,
  digits = 3
)

```


# Supplementary Table 12. Category ROI size statistics
```{r, warning=F, message=F, echo=FALSE}

S.Table12_catSelectivity_ROIsize <- list(
  list(
    data = df.ROIsize_cat_latdors,
    formula = totalvox ~ group*stream*category*hemi + (1|sub),
    filters = LMM_filters,
    analysis_name = "LMM: ROI Size (Age Group)"
  ),
  list(
    data = df.ROIsize_cat_latdors,
    formula = totalvox ~ group*category*hemi + (1|sub),
    filters = ventralLMM_filters,
    analysis_name = "Ventral LMM: ROI Size (Age Group)"
  ),
    list(
    data = df.ROIsize_cat_latdors,
    formula = totalvox ~ age*stream*category*hemi + (1|sub),
    filters = LMM_filters,
    analysis_name = "LMM: ROI Size (Age Continuous)"
  ),
  list(
    data = df.ROIsize_cat_latdors,
    formula = totalvox ~ age*category*hemi + (1|sub),
    filters = ventralLMM_filters,
    analysis_name = "Ventral LMM: ROI Size (Age Continuous)"
  )
)

# Run the function
output <- run_and_format_analysis(
  analysis_list = S.Table12_catSelectivity_ROIsize,
  file_path = output_directory,
  file_name = "S.Table12_catSelectivity_ROIsize",
  bold_p_value = 0.05,
  digits = 3
)

# CSV format
output <- run_and_format_analysis_asCSV(
  analysis_list = S.Table12_catSelectivity_ROIsize,
  file_path = output_directory,
  file_name = "S.Table12_catSelectivity_ROIsize",
  bold_p_value = 0.05,
  digits = 3
)
```


# Supplementary Table 13. Category selectivity vs FWHM statistics
```{r, warning=F, message=F, echo=FALSE}

S.Table13_catSelect_FWHM <- list(
  list(
    data = df.cat_FWHM,
    formula = meanT ~ fwhm*stream*category*hemi + (1|sub),
    filters = LMM_filters,
    analysis_name = "LMM: Category Selectivity v FWHM (No Age)"
  ),
  list(
    data = df.cat_FWHM,
    formula = meanT ~ fwhm*category*hemi + (1|sub),
    filters = ventralLMM_filters,
    analysis_name = "Ventral LMM: Category Selectivity v FWHM (No Age)"
  )
)

# Run the function
output <- run_and_format_analysis(
  analysis_list = S.Table13_catSelect_FWHM,
  file_path = output_directory,
  file_name = "S.Table13_catSelect_FWHM",
  bold_p_value = 0.05,
  digits = 3
)

# CSV format
output <- run_and_format_analysis_asCSV(
  analysis_list = S.Table13_catSelect_FWHM,
  file_path = output_directory,
  file_name = "S.Table13_catSelect_FWHM",
  bold_p_value = 0.05,
  digits = 3
)
```

# Move all bolded files to the bold directory
```{r}
# Define the destination subdirectory for bold files
bold_directory <- file.path(output_directory, "bold")
csv_directory <- file.path(output_directory, "csv")
png_directory <- file.path(output_directory, "png")

# Ensure the directories exists
if (!dir_exists(bold_directory)) {
  dir_create(bold_directory)
}

if (!dir_exists(csv_directory)) {
  dir_create(csv_directory)
}

if (!dir_exists(png_directory)) {
  dir_create(png_directory)
}

# List all files in the source directory
all_files <- dir_ls(output_directory, type = "file", recurse = FALSE)

# Filter for files with "_bold" in their names
bold_files <- all_files[grepl("_bold", all_files)]
csv_files <- all_files[grepl(".csv", all_files)]
png_files <- all_files[grepl(".png", all_files)]

# Move the bold files to the bold directory
for (file in bold_files) {
  file_move(file, file.path(bold_directory, path_file(file)))
}

for (file in csv_files) {
  file_move(file, file.path(csv_directory, path_file(file)))
}

for (file in png_files) {
  file_move(file, file.path(png_directory, path_file(file)))
}

# Print summary
cat("Moved", length(bold_files), "bold.png files to:", bold_directory, "\n")
cat("Moved", length(csv_files), "csv files to:", csv_directory, "\n")
cat("Moved", length(png_files), "png files to:", png_directory, "\n")
```



